A Decision Procedure for String Constraints with String-Integer Conversion and Flat Regular Constraints

### 2021-05-16 FMCAD2021/6_impl_exp.tex
benchmarks

The outputs of our solver can be SAT, UNSAT, B-UNSAT (short for bounded unsat) or TIMEOUT. For satisfiable cases, if a satisfying assignment is found, our solver returns ``SAT" together with the model. For unsatisfiable cases, our solver will decide whether the manually specified bound for variables is needed. The output ``UNSAT" means the formula is unsatisfiable over $\Nat$, while ``B-UNSAT" means no solution within the range. ``TIMEOUT" will be returned if the computation excesses the time limit. 
}

@@

To evaluate the performance of the {\paexp}-solver, we created two benchmark suites, ARITHMETIC, and STRINGHASH.
\begin{itemize}
\item The ARITHMETIC benchmark suite comprises the {\paexp} formulas.
%
\item The STRINGHASH benchmark suite comprises 
\end{itemize}

>>>>

The outputs of our solver can be SAT, UNSAT, B-UNSAT (short for bounded unsat) or TIMEOUT. For satisfiable cases, if a satisfying assignment is found, our solver returns ``SAT" together with the model. For unsatisfiable cases, our solver will decide whether the manually specified bound for variables is needed. The output ``UNSAT" means the formula is unsatisfiable over $\Nat$, while ``B-UNSAT" means no solution within the range. ``TIMEOUT" will be returned if the computation excesses the time limit. 
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

To evaluate the performance of the {\paexp}-solver, we created two benchmark suites, ARITHMETIC, and STRINGHASH.
%\begin{itemize}
%\item

\paragraph{The ARITHMETIC benchmark suite} 
This suite comprises four groups of randomly generated {\paexp} formulas. Each group is characterized by four parameters ($EV$, $LV$, $EI$, $LI$), where $EV, LV$ represent the number of variables with exponential occurrences and with only linear occurrences respectively, and $EI, LI$ represent the number of inequalities with exponential terms and with only linear terms respectively. 
We consider the following parameter classes, 
The ARITHMETIC benchmark suite consists of 200 randomly generated problem instances. The coefficients of exponential terms are randomly selected from the interval $[-10, 10]$ and the other coefficients/constants are randomly selected from the interval $[-10^5, 10^5]$. The two intervals are chosen with intention that the coefficients of exponential terms are smaller so that they do not always dominate the left-hand side of the inequalities.

%
%\item

\paragraph{The STRINGHASH benchmark suite} 
This suite comprises 
%\end{itemize}
